## Step 1: Install packages

```{r install packages}
install.packages("tidyverse")
install.packages("skimr")
install.packages("janitor")
```

Load the packages using the library() function:

```{r load packages}
library(tidyverse)
library(skimr)
library(janitor)
```

## Step 2: Import data

```{r load dataset}
hotel_bookings <- read_csv("hotel_bookings.csv")
```

## Step 3: Explore the data

Preview the first few rows of the dataset:

```{r head function}
head(hotel_bookings)
```

Get an overview of the data structure:

```{r str function}
str(hotel_bookings)
```

`glimpse()`: Similar to str(), but gives a more compact view of the data.

```{r glimpse function}
glimpse(hotel_bookings)
```

```{r colnames function}
colnames(hotel_bookings)
```

##Step 4: Manipulate the Data Create a new dataframe sorted by the highest lead_time:

```{r new dataframe}
hotel_bookings_v2 <-
  arrange(hotel_bookings, desc(lead_time))
head(hotel_bookings_v2)
```

We can also find out the maximum, minimum and mean lead times without sorting the whole data set using the `arrange()` function:

```{r}
max(hotel_bookings$lead_time)
min(hotel_bookings$lead_time)
mean(hotel_bookings$lead_time)
```

## Step 5: Filter the Data

Filter for city hotels:

```{r filter}
hotel_bookings_city <- 
  filter(hotel_bookings, hotel_bookings$hotel=="City Hotel")
head(hotel_bookings_city)
```

Check the average lead time for city hotels:

```{r average lead time city hotels}
mean(hotel_bookings_city$lead_time)
```

##Step 6: Group and Summarize Data Summarize the data by hotel type

```{r group and summarize}
hotel_summary <- 
  hotel_bookings %>%
  group_by(hotel) %>%
  summarise(average_lead_time=mean(lead_time),
            min_lead_time=min(lead_time),
            max_lead_time=max(lead_time))
```

Preview the summarized data:

```{r}
head(hotel_summary)
```
